Toxic Code Snippets on Stack Overflow

### 2018-11-25 cloverflow-tse/cloverflow.tex
Modified Rocco's bio a bit more.
Shortened Chaiyong's bio and restored Jens's change on Rocco's bio.

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{cragkhit.jpg}}]{Chaiyong Ragkhitwetsagul}
is a lecturer at the Faculty of Information and Communication Technology, Mahidol University, Thailand. He received the PhD degree in Computer Science at University College London, where he was part of the Centre for Research on Evolution, Search, and Testing (CREST) and Software Systems Engineering (SSE) Group. His research interests include code search, code clone detection, software plagiarism, modern code review, search-based software engineering, and mining software repositories. More info at \url{http://mucc.mahidol.ac.th/~chaiyong.rag/}.
\end{IEEEbiography}
%\vspace{-1cm}

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{cragkhit.jpg}}]{Chaiyong Ragkhitwetsagul}
is a lecturer at the Faculty of Information and Communication Technology, Mahidol University, Thailand. He received the PhD degree in Computer Science at University College London, where he was part of the Centre for Research on Evolution, Search, and Testing (CREST). His research interests include code search, code clone detection, software plagiarism, modern code review, and mining software repositories. %More info: \url{http://mucc.mahidol.ac.th/~chaiyong.rag}.
\end{IEEEbiography}
%\vspace{-1cm}
